---
title: "Installation"
format: html
editor: visual
---

## Create a GitHub Account

Create a free account at [github.com](https://github.com). Take time to consider your username-- here is some helpful [advice](https://happygitwithr.com/github-acct.html#username-advice).

## Install Git

If you do not have a current version of R or RStudio, install those first from [here](https://cloud.r-project.org/) and [here](https://posit.co/download/rstudio-desktop/). If you already have the R and RStudio installed, consider updating to the most recent versions so we can more easily troubleshoot during the workshop. You can see the version I am using and how to check your current version below:

```{r}
R.version.string
```

There are many options for installing Git. The following are just the most recommended and (generally) easiest options. Again, I'll rely on Jenny Bryan to pick up my slack here. For alternative installation methods, or if you want more information, give [Happy Git](https://happygitwithr.com/install-git.html#install-git) a visit.

Before trying to install Git, check to see if you already have it installed. Start by opening your flavor of shell (e.g., `Terminal`, `Command Prompt`) and type

```{r}
#| eval: FALSE
git --version
```

If you have Git installed, congratulations, you can skip this part.

### Windows

Install [Git for Windows](https://gitforwindows.org/).

### Mac

Install Git via the XCode command line tools by running either

```{r}
#| eval: FALSE
git --verion
git config
```

or by directly installing the XCode tools

```{r}
#| eval: FALSE
xcode-select --install
```

### Linux

#### Ubuntu/Debian

```{r}
#| eval: FALSE
sudo apt install git
```

#### Fedora/Red Hat

```{r}
#| eval: FALSE
sudo yum install git
```

## Link Git to R

The R package `usethis` allows us to configure Git in R. Install `usethis` if you have not already and set your Git credentials using the **same** username and email your used to create your GitHub account.

```{r}
#| eval: false

install.packages("usethis")

library(usethis)
use_git_config(user.name = "username", user.email = "email@cornell.edu")
```
